Implications of afforestation policies for global markets

### 2023-06-01 paper.Rmd
Update paper.Rmd

Scenarios
1) Full attainment of UN strategic plan for forests 2030 (UNFF):  This says that all deforestation will halt and there will be a 3% (120 million hectare) increase in forest area worldwide by 2030 [@sewell2020].
2) Full attainment of AFR100:  This says that there will be a 100 million hectare increase in forest area just in Sub-Saharan Africa by 2030 [@sewell2020].
3) Full attainment of goals of Bonn Challenge and New York Declaration on Forests:  This says that all deforestation will halt and there will be a 350 million hectare increase in forest area worldwide by 2030 [@sewell2020].

>>>>

Scenarios
1) Full attainment of AFR100 pledges as part of Bonn Challenge:  This says that there will be a 127.8 million hectare increase in forest area just in Sub-Saharan Africa by 2030 [@bonn2023]. To see the list of countries and the hectares pledged, please view the Excel document "Bonn Challenge-Africa".
2) Partial attainment of AFR100 pledges as part of Bonn Challenge:  This scenario analyzes full attainment for nations with no internal wars and no current wars in neighboring lands and 0% attainment in all other regions. That results in a 127.8 million hectare increase in forest area by 2030 [@bonn2023].
3) Full attainment of UN strategic plan for forests 2030 (UNFF):  This says that all deforestation will halt and there will be a 3% (120 million hectare) increase in forest area worldwide by 2030 [@sewell2020].
4) 
5) Full attainment of goals of Bonn Challenge and New York Declaration on Forests:  This says that all deforestation will halt and there will be a 350 million hectare increase in forest area worldwide by 2030 [@sewell2020].
